Scalar on Function Regression

### 2022-01-06 Presentation/slides.tex
Increment
Presentation

@@

		\begin{itemize}
			\item Continuous underlying process, where $x_n(t)$ exists $\forall t \in [T_1, T_2]$
			\item Only observed at $x_{n}(t_{j,n})$
			\item Growth curves, financial data, human perception (pitch), ...
			\item To abstract information from the curves, they must be interpretable!
			\end{itemize}
	\end{frame}

@@

@@

		\begin{itemize}
			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ (simplification - the $\xi_{j}$ do not follow a normal)
			\item $\tilde{F}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
		\end{itemize}

>>>>

 \newcommand{\independent}{\perp\!\!\!\!\perp}

@@

		\begin{itemize}
			\item Continuous underlying process, where $x_i(t)$ exists $\forall t \in [T_1, T_2]$
			\item Only observed at $x_{i}(t_{j,i})$
			\item Growth curves, financial data, human perception (pitch), ...
			\item To abstract information from the curves, they must be interpretable!
			\end{itemize}
	\end{frame}

@@

	\begin{frame}{Random Function}
		Random element is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}$
		\begin{itemize}
			\item If $\mathcal{S} = \mathbb{R}$ $\rightarrow$ X is a random variable
			\item If $\mathcal{S} = \mathbb{R}^{n}$ $\rightarrow$ X is a random vector
			\item If $\mathcal{S}$ is a space of functions, $X$ is called a random function
		\end{itemize}
	\end{frame}

	\begin{frame}{Random Function}
		Let $E$ be the index set and this can be described as
		$${\{X(t,\omega) : t \in E, \omega \in \Omega\},}$$
		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$\\
		\begin{itemize}
			\item It can be shortened to $X(t)$ by omitting $\omega$
			\item The function is realized when the $X(t)$ have been observed for every $t \in E$
		\end{itemize}
	\end{frame}

	\begin{frame}{Square Integrable Function}
		If a function $f$ satisfies:
		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
		the function $f$ is called square integrable function
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1] $
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
			\item We focus on $\mathbb{L}^{2} [0,1]$ since the dimension of the domain of our function is 1
		\end{itemize}
	\end{frame}

	\begin{frame}{Stochastic Process Perspective}
		Functional data are the sample curves observed from continuous time stochastic precess\\
		\begin{itemize}
			\item From this perspective, $X(t)$ is a random variable (?)\\
			\item $X(\cdot)$ is a collection of random variables by each time index(?)\\
			\item Realizations of a random function belong in large collection of functions
		\end{itemize}		
	\end{frame}

	\begin{frame}{Plots}
		Two plots of stock and human growth
	\end{frame}

	\begin{frame}{Plots}
		point plots to link basis expansion
	\end{frame}
	\begin{frame}{Basis Expansion}
		Basis expansion is a linear combination of functions defining a function as described:
		$$X_{i}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad 1\leq i \leq n, \forall t \in E$$
		, where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient
		\begin{itemize}
			\item To make the function smoother
			\item To replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
		\end{itemize}		
	\end{frame}

	\begin{frame}{Two Typical Types of Basis Function}
		Fourier basis function is written as
		$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
		\vspace{2\baselineskip}
		B-spline basis function is a flexible curve defined by degree and knots \\
		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula(Do you think I need to put the formula?)
	\end{frame}

	\begin{frame}{Plots of Basis Functions }
		\begin{minipage}[t]{\textwidth}
			\includegraphics[height = 3.5cm]{../Graphics/Bspline_Basis.pdf}
			\includegraphics[height = 3.5cm]{../Graphics/Fourier_Basis.pdf}
		\end{minipage}
	\end{frame}

	\begin{frame}{Trade Off between Bias and Variance}
		How do we choose the number $K$ of basis functions?
		\begin{itemize}
			\item The larger $K$, the better fit to the data with also fitting noise
			\item If $K$ is too small, it would miss some significant information that we want to estimate 
		\end{itemize}
	\end{frame}

	\begin{frame}{Trade Off between Bias and Variance}
		\begin{itemize}
			\item $\textbf{Bias}[\hat{x}(t)] = x(t) - E[\hat{x}(t)]$
			\item $\textbf{Var}[\hat{x}(t)] = E[\{\hat{x}(t) - E[x(t)]\}^2]$
			\item $\textbf{MSE}[\hat{x}(t)] = E[\{\hat{x}(t) - x(t)\}]$
			\item $\textbf{MSE}[\hat{x}(t)] = \textbf{Bias}^2[\hat{x}(t)] + \textbf{Var}[\hat{x}(t)]$
		\end{itemize}
		In the sense of that, we need to concentrate on decreasing \textbf{MSE}.
	\end{frame}

	\begin{frame}{Trade Off between Bias and Variance}
		\begin{minipage}[t]{\textwidth}
			\includegraphics[height = 7cm]{../Graphics/Trade_off.png}
		\end{minipage}
	\end{frame}

@@

		\begin{itemize}
			\item $\tilde{\xi}_{j} \sim \mathcal{N}(0,\hat{\lambda}_j)$ and $\tilde{\xi}_{j} \independent \tilde{\xi}_{k}$ for $j \neq k$
			\item Simplification: the $\xi_{j}$ do not follow a normal
			\item $\tilde{F}(\omega)(t)$, $\hat{\mu}(t)$ and $\hat{\nu}_j(t)$ are approximated as vectors in $\mathbb{R}^{401}$.
		\end{itemize}
